Exploring Transfer Learning with Fluorescence Cell Image

### 2019-11-27 paper/paper.tex
fyc

    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{paper/figures/loss.png}
    \end{subfigure}
    \caption{Results of models on training data set. Model1 represents the pretrained model with the earliest layer, Model2 with the second earliest layer and so on.}
  \end{figure}

@@

\begin{tabular}{|c|c|c|c|c|}
    \hline\\
     &Model1 & Model2&Model3&Model4 \\
     \hline\\
     Error&0.229&0.565&0.314&0.236\\
     \hline\\
     Accuracy&0.946&0.932&0.927&0.936\\
      \hline
     F1 Score&0.321&0.169&0.312&0.267\\
     \hline
\end{tabular}

{\raggedright Table 1: Results of models on test set. Model1 represents the pre-trained model with the earliest layer, Model2 with the second earliest layer and so on. \par}

>>>>

    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{paper/figures/loss.png}
    \end{subfigure}
    \caption{Results of models on training data set. Model 1 represents the pre-trained model with the earliest layer, Model 2 represents the pre-trained model with the second earliest layer and so on.}
  \end{figure}

@@

\begin{tabular}{|c|c|c|c|c|}
    \hline\\
     Model 1 & Model 2&Model 3&Model 4 \\
     \hline\\
     Error&0.229&0.565&0.314&0.236\\
     \hline\\
     Accuracy&0.946&0.932&0.927&0.936\\
      \hline
     F1 Score&0.321&0.169&0.312&0.267\\
     \hline
\end{tabular}

{\raggedright Table 1: Results of models on test set. Model 1 represents the pre-trained model with the earliest layer, Model 2 with the second earliest layer and so on. \par}
